Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
Remove comment that's no longer relevant.

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=F)
summary(pca)
screeplot(pca)
pca$rotation
@

<<pca, fig.cap="Plots of the principle components with observations. Visual Search and Paper Folding strongly contribute to both PC1 and PC2, while Figure Classification and Paper Folding strongly contributes to PC3 and Card Rotation strongly contributes to PC4", comment="|", fig.height=4.5, fig.width=4.5, warning=F, message=F, out.width='.45\\textwidth'>>=
# Just using the 4 cognitive tests and ignoring the lineups...
pca.cog.tests <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], retx=T)
summary(pca.cog.tests)
pca.cog.tests$rotation
biplot(pca.cog.tests, choices=1:2, pc.biplot=T, cex=c(.5, 1), adj=.75)
biplot(pca.cog.tests, choices=3:4, pc.biplot=T, cex=c(.5, 1), adj=.75)
@

>>>>

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])

pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=F)
summary(pca)
screeplot(pca)
pca$rotation
@

<<pca, fig.cap="Plots of the principal components with observations. Visual Search and Paper Folding strongly contribute to both PC1 and PC2, while Figure Classification and Paper Folding strongly contributes to PC3 and Card Rotation strongly contributes to PC4", comment="|", fig.height=4.5, fig.width=4.5, warning=F, message=F, out.width='.45\\textwidth'>>=
# Just using the 4 cognitive tests and ignoring the lineups...
pca.cog.tests <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], retx=T)
summary(pca.cog.tests)
pca.cog.tests$rotation
biplot(pca.cog.tests, choices=1:2, pc.biplot=T, cex=c(.5, 1), adj=.75)
biplot(pca.cog.tests, choices=3:4, pc.biplot=T, cex=c(.5, 1), adj=.75)
@
